visitation_bias

### 2021-01-11 analyses/visitation_bias.Rmd
back to laptop because rstan won't run on Windows...

# 1. Is bumble bee foraging biased? How do taxonomic, phylogenetic, and morphological bias compare -- NO, can't analyze this, these should be considered separate repsonse variables and analyzed in separate models? Are some BB species more biased than others?
## 1.1 Calculate Blüthgen's d' (i.e. visitation bias)
```{r}
# No grouping -- just plant.sp
bias_plantsp <- biaseval(visit_cover, plant.sp, site, date) %>%
  left_join(site_data) %>% # add site data
  left_join(bb_abundance) %>% # add BB abundance data
  left_join(fl_abundance) %>% # add fl abundance
  mutate(criterion = factor(rep("plant.sp", n()))) %>%
  left_join(no_plant.sp)

# Grouped by k.type.ss
bias_ktype <- biaseval(visit_cover, k.type.ss, site, date) %>%
  left_join(site_data) %>%
  left_join(bb_abundance) %>% # add BB abundance data
  left_join(fl_abundance) %>% # add fl abundance
  mutate(criterion = factor(rep("ktype", n()))) %>%
  left_join(no_ktype)

# Grouped by plant.family
bias_family <- biaseval(visit_cover, plant.family, site, date) %>%
  left_join(site_data) %>%
  left_join(bb_abundance) %>% # add BB abundance data
  left_join(fl_abundance) %>% # add fl abundance
  mutate(criterion = factor(rep("plant.family", n()))) %>%
  left_join(no_plant.family)

# Collated
bias <- bind_rows(bias_plantsp.sitedate, 
                  bias_ktype.sitedate, 
                  bias_family.sitedate) %>%
  mutate(bb.sp = factor(bb.sp),
         yday = yday(date),
         elev = elev.mean/10) 
```

>>>>

# 1. Is bumble bee foraging biased? How do taxonomic, phylogenetic, and morphological bias compare -- NO, can't analyze this, these should be considered separate repsonse variables and analyzed in separate models? Are some BB species more biased than others?
## 1.1 Calculate Blüthgen's d' (i.e. visitation bias)
```{r}
# No grouping -- just plant.sp
bias_plantsp <- biaseval(visit_cover, plant.sp, site, date) %>%
  left_join(site_data) %>% # add site data
  left_join(bb_abundance) %>% # add BB abundance data
  left_join(fl_abundance) %>% # add fl abundance
  mutate(criterion = factor(rep("plant.sp", n())))

# Grouped by k.type.ss
bias_ktype <- biaseval(visit_cover, k.type.ss, site, date) %>%
  left_join(site_data) %>%
  left_join(bb_abundance) %>% # add BB abundance data
  left_join(fl_abundance) %>% # add fl abundance
  mutate(criterion = factor(rep("ktype", n())))

# Grouped by plant.family
bias_family <- biaseval(visit_cover, plant.family, site, date) %>%
  left_join(site_data) %>%
  left_join(bb_abundance) %>% # add BB abundance data
  left_join(fl_abundance) %>% # add fl abundance
  mutate(criterion = factor(rep("plant.family", n())))

# Collated
bias <- bind_rows(bias_plantsp, 
                  bias_ktype, 
                  bias_family) %>%
  mutate(bb.sp = factor(bb.sp),
         yday = yday(date),
         elev = elev.mean/10) 
```
